Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-11-04 xrb/paper.tex
Fix merge conflicts
Added grid and streamline plots
The streamline plot needs an explanation in the paper.

\cite{cavecchi:2013,art-2015-cavecchi-etal,art-2016-cavecchi-etal} \MarginPar{need a summary}

@@

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution).  In addition to the base grid, we
use up to 3 refinement levels, the first one a factor of 4 finer than
the previous and the remaining each a factor of 2 finer than the
previous.  \castro\ subcycles in time, so the finer grids are evolved
with a finer timestep than the coarse grids.  Occasionally, the
timestep chosen at the start of a cycle will violate the CFL condition
during the advancement of the finer grids.  In this case, we restart the
finer grid evolution with a smaller timestep, subcycling within the
larger timestep hierarchy.  We use a CFL number of 0.8 for our
simulations.  
% \MarginPar{true for all?} 
The base grid for our standard
simulations is $768\times 192$ zones, and the equivalent finest grid
when 3 refinement levels are added would be $12288\times 3072$ zones.
Our standard domain is $1.2288\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$, corresponding to $10~\mathrm{cm}$ resolution
on the finest grid.  We only refine the fuel layer in the left half of
the domain at the highest resolution (and only down to densities of
$2.5\times 10^4~\gcc$), since this is where we expect the flame to
propagate.  At the start of the simulation, $3.4\%$ of the domain is
at the finest resolution.  This increases to $7.4\%$ by the end of the
simulation, because of the increase in the scale height of the atmosphere
behind the flame.  \MarginPar{add a pic of the grid to show refinement}

@@

To measure the propagation rate of the burning front, we track the
location beyond the hottest part of the flame \MarginPar{what does this mean?} where
$\dot{e}_\mathrm{nuc}$ first drops to less than $0.1 \%$ of its
maximum value. Using $0.1 \%$ of the peak value rather than the peak value
itself helps to mitigate fluctuations caused by localized fluid
motions, as the reduced value lies in a less turbulent part of the
burning region. We also average $\dot{e}_\mathrm{nuc}$ over the  \MarginPar{I think we should discuss the averaging first, before we discuss the peak value}
vertical coordinate to further dampen these fluctuations. After an
initial transient period typically spanning $\sim 3$ ms, the flame
settles into a state of steady propagation. The position data here are
well fitted by a linear function of time (as seen in Figure
\ref{fig:flame_speed}), and the resulting slope gives the velocity of
the flame front.

@@

Show the phase plots and whatever it was that Don cooked up.

@@

>>>>

\cite{cavecchi:2013,art-2015-cavecchi-etal,art-2016-cavecchi-etal,Cavecchi2017,Cavecchi2019} \MarginPar{need a summary}

@@

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution). As seen in Figure \ref{fig:grids}, 
we use up to 3 refinement levels in addition to the base grid, the first
one a factor of 4 finer than the previous and the remaining each a
factor of 2 finer than the previous. \castro\ subcycles in time, so the 
finer grids are evolved with a finer timestep than the coarse grids. 
Occasionally, the timestep chosen at the start of a cycle will violate
the CFL condition during the advancement of the finer grids. In this
case, we restart the finer grid evolution with a smaller timestep,
subcycling within the larger timestep hierarchy.  We use a CFL number
of 0.8 for our simulations.  
% \MarginPar{true for all?} 
The base grid for our standard
simulations is $768\times 192$ zones, and the equivalent finest grid
when 3 refinement levels are added would be $12288\times 3072$ zones.
Our standard domain is $1.2288\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$, corresponding to $10~\mathrm{cm}$ resolution
on the finest grid.  We only refine the fuel layer in the left half of
the domain at the highest resolution (and only down to densities of
$2.5\times 10^4~\gcc$), since this is where we expect the flame to
propagate.  At the start of the simulation, $3.4\%$ of the domain is
at the finest resolution.  This increases to $7.4\%$ by the end of the
simulation, because of the increase in the scale height of the atmosphere
behind the flame.

\begin{figure}[t]
	\plotone{grids.pdf}
	\caption{\label{fig:grids} Slice through a simulation showing the four-level
		grid structure. Note that the boxes shown are not the simulation zones, which
		span $10~\mathrm{cm}$ at the finest level, but subdomains containing
		approximately equal numbers of zones that are each managed by a separate
		MPI process. A coarse base grid extending to the upper boundary is drawn
		in white, with the green, blue, and black grids showing the jumps in
		refinement needed to fully resolve the fuel layer and underlying neutron star.}
\end{figure}

@@

To measure the propagation rate of the burning front, we track the
location beyond the hottest part of the flame\MarginPar{what does this mean?} where
$\dot{e}_\mathrm{nuc}$ first drops to less than $0.1 \%$ of its
maximum value. Using $0.1 \%$ of the peak value rather than the peak value
itself helps to mitigate fluctuations caused by localized fluid
motions, as the reduced value lies in a less turbulent part of the
burning region. We also average $\dot{e}_\mathrm{nuc}$ over the  \MarginPar{I think we should discuss the averaging first, before we discuss the peak value}
vertical coordinate to further dampen these fluctuations. After an
initial transient period typically spanning $\sim 3$ ms, the flame
settles into a state of steady propagation. The position data here are
well fitted by a linear function of time (as seen in Figure
\ref{fig:flame_speed}), and the resulting slope gives the velocity of
the flame front.

@@

{\color{red} Show whatever it was that Don cooked up. Also need to discuss the streamline plot.}

@@

\begin{figure}[t]
	\centering
	\plotone{streamlines.pdf}
	\caption{\label{fig:streamlines} Streamlines showing velocity field at time $t = 0.01~\mathrm{s}$ for the 10/10 simulation.}
\end{figure}
